Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-24 paper/main_RA-L_v1.tex
Updated abstract

\begin{abstract}
\textcolor{red}{Too long, re-write --}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space with respect to the robot's kinematic constraints. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, we prove that it stably moves towards its target and is guaranteed to obey the robot's kinematic joint limits. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system, enabling us to encode complex joint-space behaviors. We propose a method to train such complex behaviors from kinesthetic demonstrations, by learning the parameters of the LPV system. We begin by applying a latent-embedding and a probabilistic approach to discover and represent a set of local behaviors from the demonstrated motions. Then, the corresponding local joint-space behaviors are estimated by solving a convex semi-definite optimization problem that minimizes the joint velocity error from the demonstrations. Our proposed approach is validated on a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}

>>>>

\begin{abstract}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space with respect to the robot's kinematic constraints. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, we prove that it stably moves towards its target and is guaranteed to obey the robot's kinematic joint limits. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system, and we provide a method for learning behavior matrices from demonstrations. Specifically, we use dimensionality reduction to find low-dimensional behavior regions, and then estimate the parameters of the corresponding joint-space behaviors by solving a convex semi-definite optimization problem that minimizes the joint velocity prediction error from the demonstrations. Our proposed approach is validated on a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}
